Estimating duration in the presence of misclassification

### 2024-03-20 cis-imperfect-testing.tex
Tweak imperf test figs / captions

Applying the method of \cref{E-perf-test} to CIS data estimates fewer episodes with a duration of less than three weeks, compared to \cref{E-ATACCC} (see \cref{imperf-test:fig:problem-cis-estimates}).
The \cref{E-ATACCC} estimates are more reliable over the first 2--3 weeks due to them having frequent data collection here (see \cref{E-biology-data:sec:ataccc,E-ATACCC:sec:discussion}).
This suggests an issue in the estimation using CIS data.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_perfect}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimates of the survival function using CIS data alongside the ATACCC-based estimates of \cref{E-perf-test}. CIS-based has more episodes ending in the first 14 days. \label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

The qualitative increase in long episodes is robust to the choice of prior for $\ntot$, the assumed value for $\psens$ (see \cref{imperf-test:fig:cis-sensitivity}), and the choice of prior for the hazards, $\lambda_t$ (see \cref{E-perf-test:sec:parameters-priors}).
However, the survival proportion over the first 4 weeks is sensitive to these choices.
The estimate using a test sensitivity of 0.8 and $\NBc(\mu\inform, r\inform)$ give a median survival time most similar to that of \cref{E-ATACCC}.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_final}
  \caption{Duration estimates using CIS and ATACCC data.}
  \label{imperf-test:fig:cis-estimates}
\end{figure}
\begin{figure}
  \vspace{-2.5cm}
  \makebox[\textwidth][c]{\includegraphics{cis-imperfect-testing/CIS_vary}}
  \caption{%
    (A-C) Sensitivity of CIS estimates to the value of $r$, the dispersion of the prior for $\ntot$ (a larger $r$ means a more informative prior) when $\psens = 0.8$.
    (D-F) Sensitivity of CIS estimates to the value of $\psens$ when $r = r\inform$.
    A and D: median survival time, in comparison to the ATACCC-based estimate of \cref{E-ATACCC} (shown in red).
    B and E: survival at day 50, $S_\theta(50)$.
    C and F: full survival curves out to day 100.
  }
  \label{imperf-test:fig:cis-sensitivity}
  \todo[inline]{Optional improvement: Could highlight the "preferred" model which exists in both rows and is the one used subsequently, and/or include ATACCC in the far-right hand column}
\end{figure}

The estimates are most sensitive to the choice of $r$, the strength of the prior on $\ntot$.
A very weak, almost uninformative, prior on this quantity causes the posterior estimate to be much higher than the estimate from \textcite{birrellRTM2}.
When increasing the prior's strength, the posterior estimate moves towards the prior smoothly, as expected (see \cref{imperf-test:fig:ntot}).
As discussed previously, the \cref{E-ATACCC} estimates are reliable for the first 2--3 weeks, notably including the median time.
The median using $r\inform$ matched \cref{E-ATACCC}'s median estimate and is a principled choice because it is based directly on the prior work \textcite{birrellRTM2}.
Therefore, I use this estimate in the application to the CIS data.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_ntot}
  \caption{How the posterior estimate of $\ntot$ changes with the value of $r$ in the prior on $\ntot$.}
  \label{imperf-test:fig:ntot}
\end{figure}

>>>>

Applying the method of \cref{E-perf-test} to CIS data estimates fewer episodes with a duration of less than three weeks, compared to \cref{E-ATACCC} (see \cref{imperf-test:fig:problem-cis-estimates}).
The \cref{E-ATACCC} estimates are more reliable over the first 2--3 weeks due to them having frequent data collection here (see \cref{E-biology-data:sec:ataccc,E-ATACCC:sec:discussion}).
This suggests an issue in the estimation using CIS data.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_perfect}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimates of the survival function using CIS data alongside the ATACCC-based estimates of \cref{E-perf-test}. \label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

The qualitative increase in long episodes is robust to the choice of prior for $\ntot$, the assumed value for $\psens$ (see \cref{imperf-test:fig:cis-sensitivity}), and the choice of prior for the hazards, $\lambda_t$ (see \cref{E-perf-test:sec:parameters-priors}).
However, the survival proportion over the first 4 weeks is sensitive to these choices.
The estimate using a test sensitivity of 0.8 and $\NBc(\mu\inform, r\inform)$ give a median survival time most similar to that of \cref{E-ATACCC}.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_final}
  \caption{Duration estimates using CIS and ATACCC data.}
  \label{imperf-test:fig:cis-estimates}
\end{figure}
\begin{figure}
  \thisfloatpagestyle{empty}
  \makebox[\textwidth][c]{\includegraphics{cis-imperfect-testing/CIS_vary}}
  \caption[Sensitivity of CIS estimates to the prior.]{%
    (A-C) Sensitivity of CIS estimates to the value of $r$, the dispersion of the prior for $\ntot$ (a larger $r$ means a more informative prior) when $\psens = 0.8$.
    (D-F) Sensitivity of CIS estimates to the value of $\psens$ when $r = r\inform$.
    A and D: median survival time, in comparison to the ATACCC-based estimate of \cref{E-ATACCC} (shown in red).
    B and E: survival at day 50, $S_\theta(50)$.
    C and F: full survival curves out to day 100.
  }
  \label{imperf-test:fig:cis-sensitivity}
  \todo[inline]{Optional improvement: Could highlight the "preferred" model which exists in both rows and is the one used subsequently, and/or include ATACCC in the far-right hand column}
\end{figure}

The estimates are most sensitive to the choice of $r$, the strength of the prior on $\ntot$.
A very weak, almost uninformative, prior on this quantity causes the posterior estimate to be much higher than the estimate from \textcite{birrellRTM2}.
When increasing the prior's strength, the posterior estimate moves towards the prior smoothly, as expected (see \cref{imperf-test:fig:ntot}).
As discussed previously, the \cref{E-ATACCC} estimates are reliable for the first 2--3 weeks, notably including the median time.
The median using $r\inform$ matched \cref{E-ATACCC}'s median estimate and is a principled choice because it is based directly on the prior work \textcite{birrellRTM2}.
Therefore, I use this estimate in the application to the CIS data.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_ntot}
  \caption[Sensitivity of estimates of $\ntot$ to the prior.]{How the posterior estimate of $\ntot$ changes with the value of $r$ in the prior on $\ntot$.}
  \label{imperf-test:fig:ntot}
\end{figure}
